\documentclass[11pt,twoside]{amsart}
\usepackage{amssymb, amsmath, enumerate, libertine, microtype, hyperref,tikz-cd,hyperref}
\usepackage[normalem]{ulem}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\renewcommand{\labelitemi}{$\cdot$}
\usepackage{mathrsfs}
\usepackage{phaistos}
\definecolor{dark-red}{rgb}{0.4,0.15,0.15}
%   \definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
%   \definecolor{medium-blue}{rgb}{0,0,0.5}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{1}
\hypersetup{
    colorlinks, linkcolor=dark-red,
    citecolor=dark-red, urlcolor=dark-red
}


\theoremstyle{plain}
\newtheorem{prop}{Proposition}%[section]
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{thm}[prop]{Theorem}
\newtheorem{obs}[prop]{Observation}
\newtheorem{app}[prop]{Application}
\newtheorem*{MainThm}{Main Theorem}
\newtheorem{cor}[prop]{Corollary}
\newtheorem{conj}[prop]{Conjecture}
\theoremstyle{remark}
\newtheorem{rmk}[prop]{Remark}
\newtheorem{prob}{Problem}
\newtheorem{bonus}[prop]{Bonus Problem}
\newtheorem{exc}{Exercise}
\theoremstyle{definition}
\newtheorem{ex}[prop]{Example}
\theoremstyle{definition}
\newtheorem{defn}[prop]{Definition}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\kk}{\mathsf{k}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\ssC}{\mathsf{C}}

\newcommand{\id}{\operatorname{id}}
\newcommand{\Mat}{\mathsf{Mat}}

\title{Math 111: Calculus\\ Homework due Wednesday Week 14}
% uncomment the following line and add your name if you are using this as a template for solutions
% \author{Your Name}


\begin{document}
\maketitle

\begin{prob}
Let $y = y(t)$ represent the size of a population varying over time $t$. Suppose that $y$ satisfies
\[
  y' = rt(S-y)
\]
for positive constants $r,S$. This model is similar to Newton's law of cooling, but now $rt$ instead of just $r$ is multiplying $(S-y)$.
\begin{enumerate}[(a)]
\item Find the most general solution to the above differential equation.
\item What is the limit at $t\to \infty$ of $y(t)$?
\item Find the particular solution when the initial population is $2S$.
\item Find the particular solution when the initial population is $S/2$.
\end{enumerate}
\end{prob}

\begin{prob}
Suppose that a swimming pool contains 13,000 gallons of water and 350 pounds of salt. As it rains over the winter, water is drained from the pool at a rate of 225 gallons per week to keep the water level constant.

Let $s = s(t)$ denote the number of pounds of salt in the pool at time $t$ (with $t$ measured in weeks).

\begin{enumerate}[(a)]
\item In terms of $s$, what is the concentration of salt in the pool at time $t$ (in pounds/gallon)?
\item We have
\[
  s' = -(\text{number of pounds of salt lost per week}).
\]
Write a differential equation for $s'$ in terms of $s$.
\item Solve the differential equation to find $s(t)$ with initial condition $s(0) = 350$ pounds.
\item How many pounds of salt are lost after 28 weeks? Use a calculator to give an approximate solution.
\end{enumerate}

If you owned this pool, this is the amount of salt you would have to add to the pool at the beginning of the swimming season!
\end{prob}


\end{document}