\documentclass[11pt,twoside]{amsart}
\usepackage{amssymb, amsmath, enumerate, libertine, microtype, hyperref,tikz-cd}
\usepackage[normalem]{ulem}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\renewcommand{\labelitemi}{$\cdot$}
\usepackage{mathrsfs}
\usepackage{phaistos}


\theoremstyle{plain}
\newtheorem{prop}{Proposition}%[section]
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{thm}[prop]{Theorem}
\newtheorem{obs}[prop]{Observation}
\newtheorem{app}[prop]{Application}
\newtheorem*{MainThm}{Main Theorem}
\newtheorem{cor}[prop]{Corollary}
\newtheorem{conj}[prop]{Conjecture}
\theoremstyle{remark}
\newtheorem{rmk}[prop]{Remark}
\newtheorem{prob}{Problem}
\newtheorem{bonus}[prop]{Bonus Problem}
\newtheorem{exc}{Exercise}
\theoremstyle{definition}
\newtheorem{ex}[prop]{Example}
\theoremstyle{definition}
\newtheorem{defn}[prop]{Definition}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\kk}{\mathsf{k}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\ssC}{\mathsf{C}}

\newcommand{\id}{\operatorname{id}}
\newcommand{\Mat}{\mathsf{Mat}}
\newcommand{\eval}{\operatorname{eval}}
\newcommand{\colim}{\operatorname{colim}}

\title{Math 411: Topics in Advanced Analysis\\ Homework due Wednesday Week 9}
% uncomment the following line and add your name if you are using this as a template for solutions
% \author{Your Name}

\begin{document}
\maketitle

\begin{prob}
Suppose that $A$ is an LCA group. Recall that the topology on $\hat A$ has subbasis consisting of sets
\[
  P(K,U) = \{\chi\in \hat A\mid \chi(K)\subseteq U\}
\]
where $K\subseteq A$ is compact and $U\subseteq S^1$ is open. Let $U = e^{2\pi i(-1/4,1/4)}$ and show that for $K$ any compact neighborhood of $e\in A$, the set $\overline{P(K,U)}$ is a compact neighborhood of $1\in\hat A$. (It follows that $\hat A$ is locally compact, but you don't need to prove this here.)
\end{prob}

\begin{prob}
Fix a prime $p$ and give the Pr\"ufer $p$-group
\[
  \mu_{p^\infty} := \{z\in S^1\mid z^{p^n}=1\text{ for some }n\in \NN\}
\]
the subspace topology induced by the standard topology on $S^1$. We will write $\mu_{p^\infty}^{\text{sub}}$ for this topological group to remind ourselves that this not the discrete topology with which we normally endow $\mu_{p^\infty}$.
\begin{enumerate}[(a)]
\item Prove that $\mu_{p^\infty}^{\text{sub}}$ is a dense subspace of $S^1$.
\item Use (a) to prove that $\widehat{\mu_{p^\infty}^{\text{sub}}}\cong \ZZ$.
\item We have observed that $\hat \ZZ\cong S^1$, so we now know that
\[
  \widehat{\widehat{\mu_{p^\infty}^{\text{sub}}}}\cong S^1
\]
which is not isomorphic to $\mu_{p^\infty}^{\text{sub}}$. Why does this not contradict Pontryagin duality?
\end{enumerate}
\end{prob}

\begin{prob}
For $j\in \NN$, let $A_j$ be a nontrivial compact Abelian group, and let $A = \prod_{j\in \NN}A_j$. Suppose the topology on $A_j$ is induced a metric $d_j$ such that $A_j$ has diameter $1$. Define
\[
\begin{aligned}
  d\colon A\times A&\longrightarrow \RR_{\ge 0}\\
  (x,y)&\longmapsto \sum_{j\in \NN}\frac{d_j(x_j,y_j)}{2^j}.
\end{aligned}
\]
\begin{enumerate}[(a)]
\item Show that $d(x,y)$ defines a metric on $A$ that makes $A$ a compact LCA group.
\item Show that for each $j\in \NN$, the projection $A\to A_j$ is a continuous group homomorphism.
\item Show that if each $A_j$ is finite, then every continuous group homomorphism $\RR\to A$ is trivial.
\end{enumerate}
\end{prob}

\begin{prob}
For $j\in \NN$, let $A_j$ be a compact Abelian group. Suppose that for $i<j$ there is a continuous group homomorphism $\varphi_i^j\colon A_j\to A_i$. Suppose that for $i<k<j$,
\[
  \varphi_i^k\circ \varphi_k^j = \varphi_i^j.
\]
Let $\lim_j A_j$ be the set of all $x\in \prod_j A_j$ such that for all $i<j$, $\varphi_i^j(x_j)=x_i$.
\begin{enumerate}[(a)]
\item Show that $\lim A_j$ is a closed subgroup of $\prod_j A_j$. This group is called the \emph{limit} of the $A_j$.
\item Show that the projections induce continuous group homomorphisms
\[
  p_i\colon \lim A_j\longrightarrow A_i
\]
for $i\in \NN$ that satisfy $\varphi_i^k\circ p_k = p_i$ whenever $k>i$.
\item Suppose there is a compact Abelian group $A$ and a sequence of continuous group homomorphism $q_i\colon A\to A_i$ such that $\varphi_i^k\circ q_k=q_i$ for all $k>i$. Show there is a unique continuous group homomorphism $\alpha\colon A\to \lim_j A_j$ such that for each $i$,
\[
  p_i\circ \alpha = q_i.
\]
This is the \emph{universal property} of $\lim_j A_j$.
\end{enumerate}
\end{prob}

\begin{prob}
Read Exercise 5.22 from Deitmar's book or Section 3.1 of Riehl's \emph{Category theory in context} to familiarize yourself with \emph{colimits} (which Deitmar calls \emph{direct limits} and denotes $\varinjlim$). Let $(A_j,\varphi_i^j)$ be a directed system of compact Abelian groups, and let $(B_j,\psi_i^j)$ be a codirected system of discrete Abelian groups. Prove one (or both) of the following statements.
\begin{enumerate}[(a)]
\item
\[
  \widehat{\lim A_j} \cong \colim \widehat{A_j}
\]
\item
\[
  \widehat{\colim B_j}\cong \lim_j \widehat{B_j}
\]
\end{enumerate}
\end{prob}





\end{document}