\documentclass[11pt,twoside]{amsart}
\usepackage{amssymb, amsmath, enumerate, palatino, hyperref}
\usepackage[normalem]{ulem}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\renewcommand{\labelitemi}{\guillemotright}
\usepackage{mathrsfs}
\usepackage{phaistos}


\theoremstyle{plain}
\newtheorem{prop}{Proposition}%[section]
\newtheorem{lemma}[prop]{Lemma}
\newtheorem{thm}[prop]{Theorem}
\newtheorem{obs}[prop]{Observation}
\newtheorem{app}[prop]{Application}
\newtheorem*{MainThm}{Main Theorem}
\newtheorem{cor}[prop]{Corollary}
\newtheorem{conj}[prop]{Conjecture}
\theoremstyle{remark}
\newtheorem{rmk}[prop]{Remark}
\newtheorem{prob}{Problem}
\newtheorem{bonus}[prop]{Bonus Problem}
\newtheorem{exc}{Exercise}
\theoremstyle{definition}
\newtheorem{ex}[prop]{Example}
\theoremstyle{definition}
\newtheorem{defn}[prop]{Definition}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\kk}{\mathsf{k}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\ssC}{\mathsf{C}}
\newcommand{\sU}{\mathscr{U}}
\newcommand{\ol}{\overline}

\newcommand{\id}{\operatorname{id}}
\newcommand{\Int}{\operatorname{Int}}
\title{Math 544: Topology\\ Homework due Friday Week 2}
%\author{Your Name}

\begin{document}
\maketitle

\noindent Problems taken from \emph{Introduction to Topological Manifolds} are marked ITM $x$--$y$. Please review the syllabus for expectations and policies regarding homework.

\begin{prob}[ITM 2--5]
For each of the following properties, give an example of consisting of two subsets $X,Y\subseteq \RR^2$, both considered as subspaces of the Euclidean plane, together with a map $f\colon X\to Y$ that has the indicated property. (No justifications required.)
\begin{enumerate}[(a)]
  \item The map $f$ is open but neither closed nor continuous.
  \item The map $f$ is closed but neither open nor continuous.
  \item The map $f$ is continuous but neither open nor closed.
  \item The map $f$ is continuous and open but not closed.
  \item The map $f$ is continuous and closed but not open.
  \item The map $f$ is open and closed but not continuous.
\end{enumerate}
\end{prob}

\begin{prob}[ITM 2--7]
Prove Proposition 2.39: In a Hausdorff space, every neighborhood of a limit point contains infinitely many points of the set.
\end{prob}

\begin{prob}[ITM 2--10]
Suppose $f,g\colon X\to Y$ are continuous maps and $Y$ is Hausdorff. Show that the \emph{equalizer} of $f$ and $g$,
\[
  \operatorname{eq}(f,g) := \{x\in X\mid f(x)=g(x)\},
\]
is closed in $X$. Give a counterexample if $Y$ is not Hausdorff.
\end{prob}

\begin{prob}[ITM 2--14]
Prove Lemma 2.48: Suppose $X$ is a first countable space, $A$ is any subset of $X$, and $x$ is any point of $X$.
\begin{enumerate}[(a)]
  \item A point $x\in \ol A$ if and only if $x$ is a limit of a sequence of points in $A$.
  \item A point $x\in \Int A$ if and only if every sequence in $X$ converging to $x$ is eventually in $A$.
  \item The set $A$ is closed in $X$ if and only if $A$ contains every limit of every convergent sequence of points in $A$.
  \item The set $A$ is open in $X$ if and only if every sequence in $X$ converging to a point in $A$ is eventually in $A$.
\end{enumerate}
\end{prob}

\begin{prob}[ITM 2--19]
Let $X$ be a topological space and let $\sU$ be an open cover of $X$.
\begin{enumerate}[(a)]
\item Suppose we are given a basis for each $U\in \sU$ (when considered as a topological space in its own right via the subspace topology). Show that the union of all these bases is a basis for $X$.
\item Show that if $\sU$ is countable and each $U\in \sU$ is second countable, then $X$ is second countable.
\end{enumerate}
\end{prob}

\end{document}